A Review on Multi-Label Learning Algorithms

### 2018-01-13 Paper/Presentation/mll_review.tex
update presentation

%------------------------------------------------
\subsection{Problem Transformation Methods}

\begin{frame}

\frametitle{\insertsection : \insertsubsection}
\textbf{Binary Relevance}
\begin{itemize}
	\item Decompose to $q$ independent binary classification problems, $h_i(x)$
	\item Cross-train on $q$ binary training sets (one for each $y_i$)
	\item Predict labels of unseen $x$ by evaluating each classifier $h_i(x)$
	\item Output labels where  $h_i(x) > 0$ else $\underset{1 \geq i \geq q}{argmax} \{h_i(x))\}$ 
\end{itemize}

@@

\begin{frame}
\frametitle{Classifier chains}
\begin{itemize}
\item <2-> 
\begin{itemize}
\item 
\item <4-> 
\end{itemize}
\end{itemize}
\begin{itemize}
\item<5-> 
\end{itemize}

\begin{itemize}
\item <7-> 
\begin{itemize}
\item <8-> 
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
\item <2-> 
\begin{itemize}
\item 
\item <4-> 
\end{itemize}
\end{itemize}
\begin{itemize}
\item<5-> 
\end{itemize}

\begin{itemize}
\item <7-> 
\begin{itemize}
\item <8-> 
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
\item <2-> 
\begin{itemize}
\item 
\item <4-> 
\end{itemize}
\end{itemize}
\begin{itemize}
\item<5-> 
\end{itemize}

\begin{itemize}
\item <7-> 
\begin{itemize}
\item <8-> 
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------

\subsection{Alogrithm Adaptation Methods}

\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbor}
\begin{itemize}
\item <2-> 
\item <3-> 
\item <4-> 
\item<5-> 
\item <6-> 
% \item<7->
\end{itemize}
\end{frame}

@@

%\begin{figure}
%	\includegraphics[width = \textwidth, height = \textheight, keepaspectratio]{modelcharacters.png}
%	\caption{Character enhanced word representations}
%	\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}

%\begin{figure}
%	\includegraphics[width = \textwidth, height = \textheight, keepaspectratio]{modelcharacters.png}
%	\caption{Character enhanced word representations}
%	\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}

%\begin{figure}
%	\includegraphics[width = \textwidth, height = \textheight, keepaspectratio]{modelcharacters.png}
%	\caption{Character enhanced word representations}
%	\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------

@@

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\frametitle{Conclusion}
\begin{itemize}
\item 
\item 
\end{itemize}
\onslide<4->{}
\begin{itemize}
\item <5-> 
\item <6->
\item <7-> 
\end{itemize}
\end{frame}

%------------------------------------------------
\section{The end}
\begin{frame}
\Huge{\centerline{Thank you}}
\end{frame}

\end{document}

>>>>

%------------------------------------------------
\subsection{Problem Transformation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Problem Transformation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Binary Relevance}

\begin{itemize}
	\item Decompose to $q$ independent binary classification problems, $h_i(x)$
	\item Cross-train on $q$ binary training sets (one for each $y_i$)
	\item Predict labels of unseen $x$ by evaluating each classifier $h_i(x)$
	\item Output labels where  $h_i(x) > 0$ else $\underset{1 \geq i \geq q}{argmax} \{h_i(x))\}$ 
\end{itemize}

@@

\begin{frame}
\frametitle{Classifier chains}
\begin{itemize}
	\item High-order approach algorithm
	\item Transform the problem into a chain of binary classification problems
	\item Build subsequent binary classifiers upon the predictions of preceding ones
	\item A permutation function is used to specify an order to the labels
	\item Binary training set
constructed by appending each instance with its relevance
to those labels
	\item Predict relevant labels for unknown instances by iteratively traversing the classifier chain
\end{itemize}

Pros \& cons:
\begin{itemize}
	\item Effectiveness largely affected by the ordering
	\item Exploitation of label correlations
	\item Does not support parallel implementation
\end{itemize}
\end{frame}
%------------------------------------------------

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
	\item Second-order approach algorithm
	\item Transform the problem into a label ranking problem
	\item Ranking implemented by pairwise comparison techniques
	\item For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison
	\item Construct training set per label pairs considering the example's relevance
	\item For unknown instance, get the overall classifiers' votes
	\item Virtual label $y_v$ as thresholding parameter
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Smooth the class-imbalance
	\item Classifier's number grows from linear to quadratic scale
	\begin{itemize}
		\item Improvement: Exact or approximate pruning to reduce classifier's number to be queried
	\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
	\item High-order approach algorithm
	\item Decompose to an ensemble of multi-class classification problems
	\item Each component targets a random subset of $Y$, inducing a multi-class classifier by Label Powerset (LP) techniques
	\item Convert training set into a multi-class set, treating each label set as a new class
	\item Each example is reassigned with the mapped single-label participating in multi-class classifier induction
	\item For unknown $x$, counts the maximum and actual number of votes
	\item Label set is relevant when the actual number of votes exceeds
half of the maximum ones
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Incompleteness: predicts only label sets included in the training set
	\item Inefficiency: large $Y$ implies high training complexity.Improvement by combining LP and ensemble learning
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Alogrithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item First-order approach algorithm, adapting knn techniques
	\item Maximum a posteriori (MAP) rule to make prediction by reasoning and embody label info in the neighbours
	\item For new instances, $N(x)$ represents the set of its knn (uses Euclidean distance)

\end{itemize}
\end{frame}

@@

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}

\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------

@@

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\frametitle{Conclusion}
\begin{itemize}
	\item 
\end{itemize}
\end{frame}

%------------------------------------------------
\section{The end}
\begin{frame}
\Huge{\centerline{Thank you}}
\end{frame}
%------------------------------------------------
\end{document}
